HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-06-02 paper/main.tex
is_scene

\subsection{Annotation Statistics}
\label{sec:annot_stats}

@@

\begin{table}[t]
\begin{center}
{\small
\begin{tabular}{l|cccc}
 & cs & de & pl & ro \\
\hline
Sentences & 181 & 102 & 334 & 217 \\
\hline
All units & 4686   & 2793   & 8384   & 5604  \\
Kappa & 0.64   & 0.61   & 0.58   & 0.69  \\
\hline
Atomic units & 2982 & 1724 & 5386 & 3570 \\
Kappa & 0.54 & 0.29 & 0.54 & 0.50 \\
\hline
Structural units & 1602 & 1040 & 2655 & 1989 \\
Kappa & 0.31 & 0.44 & 0.33 & 0.58 \\
\end{tabular}
\caption{Inter-annotator agreement for the multiply-annotated portions of the data, as
measured by Cohen's Kappa. }
\label{tab:iaa}
}
\end{center}
\end{table}

@@

To assess whether, HUME supports the reliable annotation of long sentences,
we binned the sentences according to length and measured Kappa on each of the bins.
The Kappas for each bin (bins are 10 words wide) is presented in 
\figref{fig:iaalength}.
Results show that there is no reduction of IAA with sentence
length, except perhaps in German. Also, from \tabref{tab:iaa} the overall IAA
is quite similar (0.6-0.7) for all languages, showing good agreement.
However, there are differences observed when we break down by node type.
In particular, we see a contrast  between
Czech and Polish, where the IAA is higher for atomic than for structural units, and German and Romanian,
where the reverse is true. We also observe low IAA (around 0.3) in the cases of
German atomic units, and Polish and Czech structural units.

@@

HMEANT focuses on verbal
argument structures, ignoring other pervasive phenomena such as nominal predicates, inter-clause
relations and copula clauses. Some of the uncovered cases were already observed
in previous applications of HMEANT to languages other than English (see \perscite{birch-EtAl:2013:WMT} for German, \perscite{bojar:wu:ssst:2012} for
Czech and by \perscite{chuchunkov-tarelkin-galinskaya:2014:SSST-8} for Russian)
but the problems are also seen in English.

%This focus on verbal predicates has a number of unfortunate consequences. We show an example below:
Consider the example:

@@

The German machine translation 
is largely correct, except that the main verb ``sein'' (``be'') is omitted.
While this may be interpreted as a minor error, HMEANT will assign the
sentence a very low score, as it failed to translate the main verb.

There are however a number of other serious consequences on focusing on verbal
predicates. We conducted an analysis of the English UCCA Wikipedia
corpus (5324 sentences)
in order to assess the impact of the following problems: 
\\
\begin{inparadesc}
\item[Copula clauses] are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to conservative estimates that only consider non-auxiliary instances of ``be''.
\\
\item[Nominal argument structures,] which are ignored by  HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences.
\\
\item[Linkers] expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences, but are ignored by HMEANT.
An example where a linker is omitted in translation in our experiments is
with the source \equo{However, this review\dots}, which was translated to
the German \equo{Diese \"Uberpr\"ufung\dots} (lit. \equo{This review}).
This omission will not be taken into account by HMEANT at all\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified non-auxiliary instances of ``be'' and nouns using the NLTK standard tagger. Nominative argument structures are here defined as Scenes whose main relation is headed by a noun.}.
\end{inparadesc}

@@

We are not aware of any empirical evaluation that demonstrates that verb argument structure,
taken alone, captures the crux of the sentence semantics meanings.
% I am not sure that this is true
%The coverage of
%these and other phenomena by HUME will allow to empirically determine 
%(rather than stipulate), which semantic structures are important
%to preserve for MT evaluation, and which are less important.

@@

\paragraph{One vs. Two Structures}

HUME uses just one structural annotation (for the source) while HMEANT relies on
two independently constructed structural annotations (for both the reference and
the candidate translation)
%First of all, the annotation process is different. We semantically annotate the
%source, then automatically project it to the translation, and ask bilingual
%annotators to assess whether this projection shows a good or bad translation. In
%HMEANT, they semantically annotate both the reference and the translation, then
%align these manually, and assess to what extent they match.
%We see this difference as crucial where semantic analysis is concerned, as it
and it is often impossible to assign a semantic structure to a low quality MT output sentence.

However, HMEANT's independent annotation of the source and translation makes a stricter check
of whether the translation can be understood
than we do. HUME may be artificially boosting the perceived understandability of
the sentence by allowing access to the source.

\paragraph{Importance of Alignment}

In HMEANT, the alignment between the (reference and translation) structures is a key
part of the manual annotation. If the alignment cannot be created, the 
translation is heavily penalized.
Previous experiments with HMEANT
\parcite{bojar:wu:ssst:2012,chuchunkov-tarelkin-galinskaya:2014:SSST-8} have
suggested that sometimes, the structures of the reference and of an accurate translation
still diverge, for instance due to a different
interpretation of a PP-attachment, or the verb having an additional modifier in
%suggested that sometimes, the structures of the reference and candidate
%translations diverge without any good reason, for instance due to a different
%interpretation of a PP-attachment, the verb can have one additional modifier in
one of the structures. It would be desirable to allow updates to the structural
annotations at the alignment stage,
to avoid unduly penalization due to such spurious divergences.
%annotations also at the alignment stage
%to avoid unduly penalization due to such a spurious divergence.
The same issue was seen by HMEANT authors themselves
\parcite{lo:wu:reliability:2014}:
the 
IAA on SRL dropped from 90\% to 61\% 
when the two aligned structures were from two different annotators.

>>>>

\subsection{HUME Annotation Statistics}
\label{sec:annot_stats}

@@

\begin{table}[t]
\begin{center}
{\small
\begin{tabular}{l|cccc}
 & cs & de & pl & ro \\
\hline
Sentences & 181 & 102 & 334 & 217 \\
\hline
All units & 4686   & 2793   & 8384   & 5604  \\
Kappa & 0.64   & 0.61   & 0.58   & 0.69  \\
\hline
Atomic units & 2982 & 1724 & 5386 & 3570 \\
Kappa & 0.54 & 0.29 & 0.54 & 0.50 \\
\hline
Structural units & 1602 & 1040 & 2655 & 1989 \\
Kappa & 0.31 & 0.44 & 0.33 & 0.58 \\
\end{tabular}
\caption{Inter-annotator agreement for the multiply-annotated portions of the data,
measured by Cohen's Kappa. }
\label{tab:iaa}
}
\end{center}
\end{table}

@@

To assess whether, HUME supports the reliable annotation of long sentences,
we binned the sentences according to length and measured Kappa on each of the bins.
The Kappas for each bin (bins are 10 words wide) is presented in 
\figref{fig:iaalength}.
Results show that there is no reduction of IAA with sentence
length, except perhaps in German. Also, from \tabref{tab:iaa} the overall IAA
is quite similar for all languages, showing good agreement (0.6--0.7).
However, there are differences observed when we break down by node type.
In particular, we see a contrast  between
Czech and Polish, where the IAA is higher for atomic than for structural units, and German and Romanian,
where the reverse is true. We also observe low IAA (around 0.3) in the cases of
German atomic units, and Polish and Czech structural units.

@@

HMEANT focuses on verbal
argument structures, ignoring other pervasive phenomena such as nominal predicates, inter-clause
relations and copula clauses.
We are not aware of any empirical evaluation that demonstrates that verb argument structure,
taken alone, captures the crux of the sentence semantics meanings.\oa{do we mention here that
  Scenes in their own right correlate less with DA? maybe we should distinguish verbal and non-verbal
  scenes?} Consider the example:

%``a coronary angioplasty may not be technically possible'', which was translated by our en-de system
%to ``eine koronare Angioplastie kann nicht technisch m{\"o}glich'' (gloss: 
%a coronary angioplasty can not technically possible).

The German translation 
is largely correct, except that the main verb ``sein'' (``be'') is omitted.
While this may be interpreted as a minor error, HMEANT will assign the
sentence a very low score, as it failed to translate the main verb.

%This focus on verbal predicates has a number of unfortunate consequences. We show an example below:

@@

\com{
}

There are however a number of other serious consequences on focusing on verbal
predicates. We conducted an analysis of the English UCCA Wikipedia
corpus (5324 sentences) in order to assess the pervasiveness of three phenomena that are not
well supported by HMEANT.
First, copula clauses are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to conservative estimates that only consider non-auxiliary instances of ``be''.
Second, nominal argument structures, which are ignored by  HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences.
Third, linkers, that express an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences, but are again ignored by HMEANT.
An example where a linker is omitted in translation in our experiments is
\equo{However, this review\dots}, which was translated to
the German \equo{Diese \"Uberpr\"ufung\dots} (lit. \equo{This review}).
This omission will not be taken into account by HMEANT at all\footnote{Argument structures and linkers are explicitly marked in UCCA. Non-auxiliary instances of ``be'' and nouns are identified using the NLTK standard tagger. Nominative argument structures are defined as Scenes whose main relation is headed by a noun.}.

@@

We note that some of these issues were already observed
in previous applications of HMEANT to languages other than
English. See \perscite{birch-EtAl:2013:WMT} for German, \perscite{bojar:wu:ssst:2012} for
Czech and \perscite{chuchunkov-tarelkin-galinskaya:2014:SSST-8} for Russian.

% I am not sure that this is true
%The coverage of
%these and other phenomena by HUME will allow to empirically determine 
%(rather than stipulate), which semantic structures are important
%to preserve for MT evaluation, and which are less important.

@@

\paragraph{One Structure or Two.}
HUME only annotates the source, while HMEANT relies on
two independently constructed structural annotations, one for the reference and one
for the translation.
%First of all, the annotation process is different. We semantically annotate the
%source, then automatically project it to the translation, and ask bilingual
%annotators to assess whether this projection shows a good or bad translation. In
%HMEANT, they semantically annotate both the reference and the translation, then
%align these manually, and assess to what extent they match.
%We see this difference as crucial where semantic analysis is concerned, as it

Not annotating the translation is appealing as it is often impossible to assign a
semantic structure to a low quality translation.
On the other hand, HUME's annotation may be artificially boosting the perceived understandability
of the sentence by allowing access to the source.

%%%% UNTIL HERE %%%%
\paragraph{Alignment.}
In HMEANT, the alignment between the reference and translation structures is a key
part of the manual annotation. If the alignment cannot be created, the 
translation is heavily penalized.
Previous experiments with HMEANT
\parcite{bojar:wu:ssst:2012,chuchunkov-tarelkin-galinskaya:2014:SSST-8} have
suggested that sometimes, the structures of the reference and of an accurate translation
still diverge, for instance due to a different
interpretation of a PP-attachment, or the verb having an additional modifier in
%suggested that sometimes, the structures of the reference and candidate
%translations diverge without any good reason, for instance due to a different
%interpretation of a PP-attachment, the verb can have one additional modifier in
one of the structures. It would be desirable to allow updates to the structural
annotations at the alignment stage,
to avoid unduly penalization due to such spurious divergences.
%annotations also at the alignment stage
%to avoid unduly penalization due to such a spurious divergence.
The same issue was seen by HMEANT authors themselves
\parcite{lo:wu:reliability:2014}:
the 
IAA on SRL dropped from 90\% to 61\% 
when the two aligned structures were from two different annotators.
